Pushdown Control-Flow Analysis via Refunctionalization (Functional Pearl)

### 2018-02-26 paper.tex
update

\subsubsection{Single-step Evaluation}
Before go into describing how the machine evaluates expressions, we firstly define several helper functions.
As we mentioned in section \ref{anfsyntax}, the atomic expressions are either a variable, or
a literal \texttt{lambda} term. So the helper function \texttt{atomicEval} handles these two
cases and evaluates atomic expressions to closures in a straightforward way.
The \texttt{alloc} function generates a fresh address, and always allocates an unique integer under the domain
of store.
The \texttt{isAtomic} function is used as a predicate of whether the expression is atomic.

@@

\subsubsection{Single-step Evaluation}

@@

>>>>

\subsubsection{Single-step Transition}
Before go into describing how the machine evaluates expressions, we firstly define several helper functions.
As we mentioned in section \ref{anfsyntax}, the atomic expressions are either a variable, or
a literal \texttt{lambda} term. So the helper function \texttt{atomicEval} handles these two
cases and evaluates atomic expressions to closures in a straightforward way.
The \texttt{alloc} function generates a fresh address, and always allocates an unique integer under the domain
of store.
The \texttt{isAtomic} function is used as a predicate of whether the expression is atomic.

@@

\subsubsection{Single-step Transition}

@@

for plain direct-style, the apply handles more cases.
